An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-28 VLDB2026/main.tex
Update main.tex

\textit{\textbf{Index construction time.}}
\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN. PASE and VBASE only support single-threaded builds, and PASE is the slowest to build because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster. ACORN-$\gamma$  has a large computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates. The build time on some datasets even exceeds that of single-threaded VBASE. }

@@

	\textit{Single-Thread Search.}  
	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions,} search often requires traversing larger candidate sets or deeper graph paths. This leads to increased computational cost and a sharp QPS (queries per second) drop for most methods. Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency. \textcolor{violet}{Puck and CAPS perform relatively well on some datasets. Partition-based methods have limitations regarding different vector data distributions, and how to configure different partitions for different datasets remains a challenge. However, this also demonstrates that IVF-based methods are still very promising for hybrid queries.}

>>>>

\textit{\textbf{Index construction time.}}
\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN-$\gamma$. PASE and VBASE only support single-threaded builds, and PASE is the slowest to build because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster. ACORN-$\gamma$  has a large computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates. The build time on some datasets even exceeds that of single-threaded VBASE. }

@@

	\textit{Single-Thread Search.}  
	\textcolor{violet}{As shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}, under near-perfect recall (recall approaching 1) conditions,} search often requires traversing larger candidate sets or deeper graph paths. This leads to increased computational cost and a sharp QPS drop for most methods. Despite this, UNG maintains high QPS due to its LNG structure, which eliminates unnecessary online filtering of irrelevant attributes, thereby improving query efficiency. \textcolor{violet}{Puck and CAPS perform relatively well on some datasets. Partition-based methods have limitations regarding different vector data distributions, and how to configure different partitions for different datasets remains a challenge. However, this also demonstrates that IVF-based methods are still very promising for hybrid queries.}
